Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-24 WSSSPE1_report/WSSSPE1_summary_report.tex
Very minor typo

Career path issues also came up repeatedly, starting in the first
keynote (\S\ref{sec:keynote1}), where Phil Bourne used the term ``the
Google Bus'' to describe the issue of well-trained software
development staff in academic labs choosing to leave science and to
work instead for technology firms, especially Google, which happens in
large enough numbers that Google operates a bus every day to its
nearest offices (and hence staff who leaves academia in this way does
not even have to physically move).

>>>>

Career path issues also came up repeatedly, starting in the first
keynote (\S\ref{sec:keynote1}), where Phil Bourne used the term ``the
Google Bus'' to describe the issue of well-trained software
development staff in academic labs choosing to leave science and to
work instead for technology firms, especially Google, which happens in
large enough numbers that Google operates a bus every day to its
nearest offices (and hence staff who leaves academia in this way do
not even have to physically move).
